### 2025-01-31 OurWork/our_article/MCM_article/article_file.tex
赛后文件整理

    food supply has become one of the most pressing global issues. 

@@

    the existing arable land area is insufficient to meet the food demand. 

@@

    Therefore, the converted forest area must undergo a long process of ecological reconstruction. 
    However, due to the influence of human activities during this process, 
    the post-clearing forest ecosystem can no longer return to its original state, 
    but instead continuously undergoes succession into a stable agricultural ecosystem. 
    To achieve both economic and ecological benefits and fulfill sustainable development goals, 
    it is necessary to examine the ecological succession from converted forest to agricultural ecosystems and explore how green agriculture can bring dual benefits in terms of economic and ecological indicators.

@@

        \item \textbf{Impact of removing chemicals}: After the ecosystem matures, humans will attempt to remove chemicals. The model should assess the stability of the ecosystem after herbicides are removed, with the effects reflected through producers and consumers.

@@

      \item Initially, we utilized difference equation to construct Model I: 

@@

         where two crops of rice are planted each year in the farmland.\\

@@

        For simplification of the model, 
        the biomass change of the rice population during each overlapping period is represented 
        by a biomass step function at specific time points in the mathematical model (i.e., the system of difference equations). 
        Since $t=0$ corresponds to the start of the first planting season, with one year assumed to have 52 weeks, 
        and each week being a time step, based on the rice production pattern \figurename~\ref{fig:PlantModePlus}, 
        we define the step moments at week 0, week 17, and week 34 of each year. The biomass of rice at these times follows:

@@

        \begin{equation}
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1, k,n\ are\ positive\ integers)
        \end{equation}
        The difference equation for insect biomass is modified as follows:
        \begin{equation}
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t} = r_{ins} W_{ins} \left[ 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} + W_{stw} \right)} \right] - \frac{A_{ins\rightarrow bd} W_{ins} W_{bd}}{1 + B_{ins\rightarrow bd} W_{ins}}
        \end{equation}

      \subsubsection{Seasonality}
        The seasonal influences primarily include factors such as light, 
        climate (temperature, precipitation), and biological habits, 
        all of which have significant direct effects on both $r$ and $\mathscr{K}$ within populations. 
        Considering that many of these factors are difficult to quantify precisely, 
        we set sinusoidal perturbations in the periodic parameter $p(T)$ as follows\cite{GAKKHAR20061239}:

@@

        Again, for the sake of model simplification, we assume \( \mu_{Fr_i} = \xi_{i} C_{Is_i} \).
      \subsubsection{Random Factors}
        Considering the influence of random factors in nature, we introduce Gaussian white noise \(\sigma_i\) for each population.

@@

      \subsubsection{Multiple Digestion Delay}
        Due to the time required for energy flow, 
        the impacts of different predation relationships in the food web on system dynamics are actually asynchronous \cite{GUO20142850}. 
        Considering this asynchrony, 
        we introduce multiple digestion delays corresponding to the digestion periods of the consumer-eat-producer and predator-eat-consumer interactions, 
        referred to as the producer digestion delay (PDD) and consumer digestion delay (CDD), respectively.

@@

        \begin{equation}
        L_i' = -\frac{r_i}{t - \tau_i} \cdot \frac{D_i W_i^2}{1 + E_i \cdot \Sigma_{\text{food}} \gamma_i W_{i_j}}
        \end{equation}

        where \(\tau_i\) is the digestion delay factor of population \(i\), and \(D_i, E_i\) are the corresponding environmental parameters for population \(i\).
    \subsection{CAGED Model Considering Reemergence}
      As the ecosystem gradually matures, 
      previously existing populations will re-enter the system. 
      We assume that when the biomass of the prey species reaches a certain threshold,
      \begin{equation}
      E_{frg}W_{ins}>Threshold_{frg}
      \end{equation}
      \begin{equation}
      E_{snk}\sum_{i=food}{c_{i}W_{i}}>Threshold_{snk}
      \end{equation} 
      the species will migrate into the ecosystem, forming a more complex food web. 
      In our model, we only consider the migration of frogs and snakes. 
      After their migration, the previously constructed equations are applicable to describe their biomass dynamics 
      (assuming they are not affected by chemicals).
    \subsection{Model III: SAGED Model}
      SAGED Model represents Sustainable Agricultural Ecosystem Dynamics Model.
      When the food web becomes sufficiently complex, 
      humans can begin making agricultural decisions. 
      The agricultural decision considered in our model involves removing herbicides and insecticides, 
      while introducing bats and ducks.

      Bats play a role in promoting pollination; thus, the pollination factor becomes:

@@

      Besides this, the modified model only requires the removal of chemicals from the CAGED model, 
      and the introduction of two new populations to form the ultimate food web as Figure \ref{fig:food_web_green}.
      \begin{figure}[H]
        \begin{minipage}[b]{0.45\linewidth}
          \centering
          \includegraphics[height=6cm, keepaspectratio]{images/food_web_chem.pdf}
          \caption{Traditional Mode}
          \label{fig:food_web_chem}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}[b]{0.45\linewidth}
            \centering
            \includegraphics[height=6cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
            \caption{Green Mode}
            \label{fig:food_web_green}
        \end{minipage}
      \end{figure}
  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the models.
    In the models below, the unit of biomass(considering the entire farm) is kg and the unit of time is week.

@@

      \subsection{Comparison between S3 and S4: The Dependency of the Chemical-Agriculture Model on Chemicals}
      After species migration, we consider removing chemicals and compare the ecosystem's situation in the two periods. 
      The result is shown in Figure \ref{fig:S4}.
      \begin{figure}
        \centering
        \includegraphics[width=0.7\linewidth]{images/P4_producers.png}
        \caption{Dynamics after Removing Chemicals}
        \label{fig:S4}
      \end{figure}

@@

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.75\linewidth]{images/Change_init.png}
        \caption{Impact of Initial Biomass Density Changes on System Dynamics}
        \label{fig:Change_init}
      \end{figure}

@@

    \begin{figure}[H]
      \includegraphics[width=\linewidth]{images/Change_all.png}
      \caption{Impact of Changes in Key Environmental Parameters on System Dynamics}
      \label{fig:Change_all}
    \end{figure}

>>>>

    agriculture has become one of the most pressing global issues. 

@@

    the existing arable land area is insufficient to meet the agricultural demand. 

@@

    Therefore, the converted forest area must undergo a long process of ecological reconstruction, going through continuously succession into a stable agricultural ecosystem with the effect of farming activities. To achieve both economic and ecological benefits and fulfill sustainable development goals, it is necessary to analyze the ecological succession from converted forest to agricultural ecosystems and explore how green agriculture can bring dual benefits in terms of economic and ecological indicators.

@@

        \item \textbf{Impact of removing chemicals}: After the ecosystem matures, humans attempt to remove chemicals. The model should assess the stability of ecosystem after herbicides are removed, with the effects reflected through producers and consumers.

@@

      \item Initially, we utilized differential equation to construct Model I: 

@@

         where three crops of rice are planted each year in the farmland.\\

@@

        For simplification of the model, 
        the biomass change of the rice population during each overlapping period is represented 
        by a biomass step function at specific time points in the mathematical model (i.e., the system of differential equations). 
        Since $t=0$ corresponds to the start of the first planting season, with one year assumed to have 52 weeks, 
        and each week being a time step, based on the rice production pattern \figurename~\ref{fig:PlantModePlus}, 
        we define the step moments at week 0, week 17, and week 34 of each year. The biomass of rice at these times follows:

@@

        \begin{equation}
          n = 52k, 52k+17, 52k+34, \quad (k \geqslant 0, \, n \geqslant 1, k,n\ are\ positive\ integers)
        \end{equation}
        The differential equation for insect biomass is modified as follows:
        \begin{equation}
          \frac{\mathrm{d}W_{ins}}{\mathrm{d}t} = r_{ins} W_{ins} \left[ 1 - \frac{D_{ins} W_{ins}}{1 + E_{ins} \left( 0.6 W_{crp} + 0.4 W_{wd} + W_{stw} \right)} \right] - \frac{A_{ins\rightarrow bd} W_{ins} W_{bd}}{1 + B_{ins\rightarrow bd} W_{ins}}
        \end{equation}

      \subsubsection{Seasonality}
        The seasonal influences primarily include factors such as light, 
        climate (temperature, precipitation), and biological habits, 
        all of which have significant direct effects on both $r$ and $\mathscr{K}$ within populations. 
        Considering that many of these factors are difficult to quantify precisely, 
        we refer to the seasonally-varying dynamic equations modeled by Sunita Gakkhar and Brahampal Singh \cite{GAKKHAR20061239}, 
        setting sinusoidal perturbations in the periodic parameter $p(T)$ as follows:

@@

        Again, for the sake of model simplification, we assume \( \mu_{Fr_i} = \xi_{i} C_{Is_i} \).
      \subsubsection{Random Factors}
        Considering the influence of random factors in nature, we introduce Gaussian white noise $\sigma_i$ for each population, which is appended to each corresponding equation as an adding term.

@@

      \subsubsection{Multiple Digestion Delay}
        Due to the time required for energy flow, the impacts of different predation relationships in the food web on system dynamics are actually asynchronous. 
        Considering this asynchrony, we refer to the Leslie-Gower type of the food chain system with multiple delays modeled by Lei Guo, Zi-Gen Song and Jian Xu \cite{GUO20142850}, 
        introducing multiple digestion delays corresponding to the digestion periods of the consumer-eat-producer and predator-eat-consumer interactions, 
        which can be described as the producer digestion delay (PDD) and consumer digestion delay (CDD), respectively.

@@

        \begin{equation}
        \frac{dL_i}{dt} = -\frac{r_i}{t - \tau_i} \cdot \frac{D_i W_i^2}{1 + E_i \cdot \Sigma_{\text{food}} \gamma_i W_{i_j}}
        \end{equation}

        where \(\tau_i\) is the digestion delay factor of population \(i\), and \(D_i, E_i\) are the corresponding environmental parameters for population \(i\).
    \subsection{CAGED Model Considering Reemergence}
      As the ecosystem gradually matures, 
      previously existing populations will re-enter the system. 
      We assume that when the biomass of the prey species reaches a certain threshold,
      \begin{equation}
      E_{frg}W_{ins}>Threshold_{frg}
      \end{equation}
      \begin{equation}
      E_{snk}\sum_{i=food}{c_{i}W_{i}}>Threshold_{snk}
      \end{equation} 
      the species will migrate into the ecosystem, forming a more complex food web. 
      In our model, we only consider the migration of frogs and snakes. 
      After their migration, the previously constructed equations are applicable to describe their biomass dynamics 
      (assuming they are not affected by chemicals).
      At the same time, due to changes in the food web structure caused by the migration of new species, 
      the equations for insects and birds in the model have been modified. 
      Here, the aforementioned considerations are summarized, 
      and the differential equations for all components in the model are presented as follows: 
      (In this context, herbicides are treated as a type of herbivore that feeds on weeds, incorporated as part of the summation terms in their respective differential equations.)
      \begin{align}
        \frac{\mathrm{d}W_i}{\mathrm{d}t}=f_{pol}\boldsymbol{r}_iW_i\left( 1+\sigma _i-\frac{W_i+\beta _{i\rightarrow j}W_j}{\mathscr{K} _i\mu _{Fr_i}} \right) -\sum_{herb\rightarrow j}{\frac{A_{i\rightarrow j}W_iW_j}{1+B_{i\rightarrow j}W_i}}
      \end{align}
      \begin{equation}
        \begin{split}
        \frac{\mathrm{d}W_{ins}}{\mathrm{d}t}=\boldsymbol{r}_{ins}W_{ins}\left( 1+\sigma _{ins}-\frac{D_{ins}W_{ins}}{1+E_{ins}\left[ \left( 0.6-\lambda _{ptc} \right) W_{crp}+\left( 0.4+\lambda \right) W_{wd} \right]}\cdot \frac{1}{t-\tau _{ins}} \right)\\
        -\frac{A_{ins\rightarrow bd}W_{ins}W_{bd}}{1+B_{ins\rightarrow bd}W_{ins}}-\frac{A_{ins\rightarrow frg}W_{ins}W_{frg}}{1+B_{ins\rightarrow frg}W_{ins}}-\frac{A_{ptc}W_{ins}W_{ptc}}{1+B_{ptc}W_{ins}}&\hphantom{\sigma _{ins}-\frac{D_{ins}W_{ins}}{1+E_{ins}\left[ \left( 0.6-\lambda _{ptc} \right) W_{crp}+\left( 0.4+\lambda \right) W_{wd} \right]}}
        \end{split}
      \end{equation}
        \begin{align}  
        \frac{\mathrm{d}W_k}{\mathrm{d}t}=\boldsymbol{r}_kW_k\left( 1+\sigma _k-\frac{D_kW_k}{\left( t-\tau _k \right) \left( 1+E_k\cdot \sum_{l=food}{\gamma _lW_{k_l}} \right)} \right) -\sum_{m=pred}{\frac{A_{k\rightarrow m}W_kW_m}{1+B_{k\rightarrow m}W_k}}
      \end{align}
    \subsection{Model III: SAGED Model}
      SAGED Model represents Sustainable Agricultural Ecosystem Dynamics Model.
      When the food web becomes sufficiently complex, 
      humans can begin making agricultural decisions. 
      The agricultural decision considered in our model involves removing herbicides and insecticides, 
      while introducing bats and ducks.
      \begin{figure}[H]
        \begin{minipage}[b]{0.45\linewidth}
          \centering
          \includegraphics[height=4.5cm, keepaspectratio]{images/food_web_chem.pdf}
          \caption{Traditional Mode}
          \label{fig:food_web_chem}
        \end{minipage}
        \hspace{0\linewidth}
        \begin{minipage}[b]{0.45\linewidth}
            \centering
            \includegraphics[height=4.5cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
            \caption{Green Mode}
            \label{fig:food_web_green}
        \end{minipage}
      \end{figure}
      Bats play a role in promoting pollination; thus, the pollination factor becomes:

@@

      Besides this, the modified model only requires the removal of chemicals from the CAGED model, 
      and the introduction of two new populations to form the ultimate food web as Figure \ref{fig:food_web_green}.

  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the models. 
    We use MATLAB Simulink to simulate the system's dynamics. 
    For computational convenience and efficiency, 
    we utilize difference equations with an interval of one week as a substitute for differential equations. 
    In the models below, the unit of biomass (considering the entire farm) is kg and the unit of time is week.

    Table \ref{tab:Parameters} lists the key environmental parameters, which are applicable to all subsequent models.
    \begin{table}[H]
      \centering
      \caption{Parameters}
      \begin{tabular}{lccccccccc}
        \toprule
        \rowcolor{customcolor!40} % 设置背景颜色
        Parameters & $\mathscr{K}_{crp}$ & $\mathscr{K}_{wd}$ & $r_{crp}$ $r_{wd}$ & $\beta_{crp\rightarrow wd}$ & $\beta_{wd\rightarrow crp}$ & $\sigma$ & 0.05 & $W_{crp}$ & $W_{wd}$\\
        \midrule
        Values & 30000 & 24000 & 0.32 & 0.44 & 0.4 & 0.3 & 0.05 & 2000 & 1000\\
        \bottomrule
      \end{tabular}
      \label{tab:Parameters}
    \end{table}

@@

      \subsection{Comparison between S3 and S4: The Dependency of the Chemical-Agriculture Model on Chemicals}
      After species migration, we consider removing chemicals and compare the ecosystem's situation in the two periods. 
      The result is shown in Figure \ref{fig:S4}.
      \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{images/P4_producers.png}
        \caption{Dynamics after Removing Chemicals}
        \label{fig:S4}
      \end{figure}

@@

      \begin{figure}[H]
        \centering
        \includegraphics[width=0.6\linewidth]{images/Change_init.png}
        \caption{Impact of Initial Biomass Density Changes on System Dynamics}
        \label{fig:Change_init}
      \end{figure}

@@

    \begin{figure}[ht]
      \centering
      \includegraphics[width=\linewidth]{images/Change_all.png}
      \caption{Impact of Changes in Key Environmental Parameters on System Dynamics}
      \label{fig:Change_all}
    \end{figure}
